treats manual

### 2023-04-28 inst/gitbook/index.Rmd
Verbose example much improved
To finish!

# `treats`: disparity and diversity simulations.

Simultaneously simulate diversity (i.e. phylogenetic trees) and disparity  diversity (and the interaction between them).

@@

<!-- %NC: I think here you need an example of use case as it's not immediately obvious what the package is for... -->

>>>>

# `treats`: trees and traits simulations.

Simultaneously simulate phylogenetic trees and traits (and the interaction between them).

@@

Ar Macarface is studying the evolution of mammalian disparity (i.e. diversity of shapes) across the Cretaceous-Palaeogene mass extinction event (K-Pg - 66 million years ago).
They observe a decrease of morphological disparity after the extinction event followed by a sharp increase of disparity.
However Ar is also prudent and wants to test whether their observed pattern is just an artifact of the data or actually showing some effect of the K-Pg extinction on mammalian evolution.
First they need to check whether changes in disparity can actually be discernables due to an extinction event (i.e. if an extinction event happens, would it be possible to detect a change in disparity)?
Second they want to know whether these changes are due to changes are due to the mass extinction event being selective or not.

The [getting started](#kpgexample) section actually shows how do implement this example in `treats` in details.
